Extended Data

### 2022-02-03 doc/manuscript/Dow_manuscript_Nature.Rmd
address an R2 concern

Dominant tree species were cored at both SCBI[@helcoski_growing_2019;@bourg_initial_2013] and Harvard Forest[@alexander_potential_2019; @dye_comparing_2016; @finzi_carbon_2020] following sampling designs that covered a broad range of DBH.
We analyzed records for the ring- and diffuse- porous species at each site (`r  EDT_species`), but excluded species with other xylem architectures (*Juglans nigra* L. at SCBI, *Tsuga canadensis* at Harvard Forest).
We studied a total of `r n_cores_focal_sites` cores which included `r n_chronologies_SCBI` species at SCBI and `r n_chronologies_HF` species at Harvard Forest (`r  EDT_species`).

>>>>

Dominant tree species were cored at both SCBI[@helcoski_growing_2019;@bourg_initial_2013] and Harvard Forest[@alexander_potential_2019; @dye_comparing_2016; @finzi_carbon_2020] following sampling designs that covered a broad range of DBH.
We analyzed records for the ring- and diffuse- porous species at each site (`r  EDT_species`), but excluded semi-ring porous species (e.g., *Juglans nigra* L. at SCBI) and conifers (e.g., *Tsuga canadensis* at Harvard Forest).
We studied a total of `r n_cores_focal_sites` cores which included `r n_chronologies_SCBI` species at SCBI and `r n_chronologies_HF` species at Harvard Forest (`r  EDT_species`).
